An example Bayesian data analysis with PyMC:\\The TFR-HDI controversy

### 2011-07-04 tex/paper.tex
visualize data

  \subsection*{Data Preparation in data.py}
  File src/data.py holds all of the code for loading and preparing the
  data; it is relatively simple, although it could be simpler.  An
  important task for future labor is building a minimal set of data
  manipulation tools for Python that provides each routine task for
  tabular data manipulaion in a single easy-to-read command.

  For example, the 3 lines necessary to prepare the HDI data are three
  times too many lines, and more than three times too complicated.
  STATA and R provide single-line commands to accomplish this common
  task of translating from a panel data format to an extensive form.

  \subsection*{Yet another sub-heading for this section}
    Text for this sub-section \ldots

>>>>

  \subsection*{Data Preparation in data.py}
  File src/data.py holds all of the code for loading and preparing the
  data; it is relatively simple, although it could be simpler
  (Fig.~\ref{src/data.py}).  An important task for future labor is
  building a minimal set of data manipulation tools for Python that
  provides each routine task for tabular data manipulaion in a single
  easy-to-read command.

  For example, the 3 lines necessary to prepare the HDI data are three
  times too many lines, and more than three times too complicated.
  STATA and R provide single-line commands to accomplish this common
  task of translating from a panel data format to an extensive form.
\begin{figure}
  \begin{verbatim}
import pylab as pl

all_data = pl.csv2rec('nature08230-s2.csv')

years = range(1975, 2006)
hdi = [d['hdi%d'%y] for y in years for d in all_data]
hdi = pl.ma.masked_array(hdi, pl.isnan(hdi))

tfr = [d['tfr%d'%y] for y in years for d in all_data]
tfr = pl.ma.masked_array(tfr, pl.isnan(tfr))
\end{verbatim}
\caption{Listing of src/data.py}
\label{src/data.py}
\end{figure}
  \subsection*{Yet another sub-heading for this section}
    Text for this sub-section \ldots
